Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?

### 2022-09-30 SIOP2023/Counts/Submission_ResourceCount.tex
updating formatting

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?},
  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata Garcia Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\shorttitle{O*Net JDR}

@@

The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored. 568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources. The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.

@@

@@

The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes. Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption'', Schaufeli et al., 2002), workplace stress (``an individual state characterized by a combination of high arousal and displeasure'', p.~15, Pejtersen et al., 2010) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work'', p.~197; Kristensen et al., 2005). Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) would activate a positive state -- that of engagement. In contrast, number of characteristics of one's job appraised as a hindrance demand (i.e., inhibit growth, learning and goal achievement) would activate a negative state -- here, stress.

@@

We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), but from within the unifying framework of O\emph{Net. Here, we focus on the relationship between O}Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S. workforce representative sample.

@@

A sample using a Prolific panel resulted in 785 individuals who initially accessed the survey link. Of those,112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021). Additional screening using four embedded attention checks resulted in the retention of 568 respondents. A total of 13.57\% had been in their job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years. Reported ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53). Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%). Jobs were classified into the International Standard Classification of Occupations (ISCO) via the package labourR (Kouretsis et al., 2020). Modify or omit?

@@

Characteristics, Demands, and Resources. Our analyses included items within O\emph{Net's classifications of ``work activity'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'': 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
Other than minor grammatical editing (for example, changing ``the'' to ``you''), we retained the O*Net wording for our item stems. We used O*Net's response scales, several of which were unique across items, but all shared the same 1 to 5 scale options. Subsequent to providing ratings of whether or not an O}Net characteristic was relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) . . . this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) . . . this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) . . . this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

\hypertarget{stress.-three-items-taken-from-the-copenhagen-psychosocial-questionnaire-burr-et-al.-2019.-obtained-alpha-was-.85-in-this-sample.}{%
\paragraph{\texorpdfstring{\emph{Stress}. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.}{Stress. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.}}\label{stress.-three-items-taken-from-the-copenhagen-psychosocial-questionnaire-burr-et-al.-2019.-obtained-alpha-was-.85-in-this-sample.}}

\hypertarget{burnout.-four-items-were-taken-from-the-copenhagen-psychosocial-questionnaire-burr-et-al.-2019.-alpha-was-0.85-in-this-sample.}{%
\paragraph{\texorpdfstring{\emph{Burnout}. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.}{Burnout. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.}}\label{burnout.-four-items-were-taken-from-the-copenhagen-psychosocial-questionnaire-burr-et-al.-2019.-alpha-was-0.85-in-this-sample.}}

\hypertarget{engagement.-the-18-item-engagement-measure-was-recently-developed-russell-et-al.-2022-with-the-authors-specifying-three-subscales-which-yielded-current-sample-ux3b1s-of-0.68-absorption-and-0.80-vigor-and-0.90-dedication.-for-the-purposes-of-the-current-study-we-focused-on-an-overall-engagement-score-18-item-aggregate-ux3b1-0.91.}{%
\paragraph{\texorpdfstring{\emph{Engagement}. The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α's of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication). For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).}{Engagement. The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α's of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication). For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).}}\label{engagement.-the-18-item-engagement-measure-was-recently-developed-russell-et-al.-2022-with-the-authors-specifying-three-subscales-which-yielded-current-sample-ux3b1s-of-0.68-absorption-and-0.80-vigor-and-0.90-dedication.-for-the-purposes-of-the-current-study-we-focused-on-an-overall-engagement-score-18-item-aggregate-ux3b1-0.91.}}

@@

We used R (Version 4.0.3; R Core Team, 2020) and the R-packages careless (Version 1.1.3; Yentes \& Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust \& Barth, 2020), and tinylabels (Barth, 2021) for all analyses. Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands. Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
Correlations, means and standard deviations among all study variables are presented in Table 1. Results reveal a positive association between resources and engagement (r = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively). Challenge demands were positively associated with engagement (r = .31; H2a), but were unrelated to stress or burnout (H2b and H2c). Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c). To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands. First, regarding engagement (F(3, 564) = 26.41, p \textless{} .001), the total resources (beta = ??) was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table 2). Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, p = .060 (see Table 3). Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, p = .349. See Table 4.

In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.

There were 568 retained respondents.

@@

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:correlation_table}Focal variable correlations (counts data).}

\begin{tabular}{llllllll}
\toprule
 & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
\midrule
1. resource & - &  &  &  &  & 36.02 & 13.26\\
2. hindrance & .23*** & - &  &  &  & 13.09 & 13.62\\
3. challenge & .86*** & .22*** & - &  &  & 35.64 & 13.63\\
4. burnout & .05 & .04 & .07 & - &  & 3.04 & 0.87\\
5. stress & .06 & .09* & .08 & .70*** & - & 2.59 & 0.97\\
6. engagement & .34*** & .01 & .31*** & -.35*** & -.30*** & 4.04 & 0.83\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{verbatim}
## 
## Call:
## lm(formula = engagement ~ hindrance + challenge + resource, data = data22)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -2.40431 -0.50713  0.02842  0.55010  2.05201 
## 
## Coefficients:
##              Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  3.276423   0.096574  33.926  < 2e-16 ***
## hindrance   -0.004436   0.002460  -1.803 0.071918 .  
## challenge    0.004175   0.004728   0.883 0.377613    
## resource     0.018672   0.004868   3.836 0.000139 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.7763 on 564 degrees of freedom
## Multiple R-squared:  0.1232, Adjusted R-squared:  0.1185 
## F-statistic: 26.41 on 3 and 564 DF,  p-value: 5.394e-16
\end{verbatim}

\begin{verbatim}
## 
## Call:
## lm(formula = burnout ~ hindrance + challenge + resource, data = data22)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -2.23967 -0.64759 -0.04747  0.65173  2.10310 
## 
## Coefficients:
##              Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  2.895053   0.107671  26.888   <2e-16 ***
## hindrance    0.001843   0.002743   0.672    0.502    
## challenge    0.006290   0.005271   1.193    0.233    
## resource    -0.002843   0.005427  -0.524    0.601    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.8655 on 564 degrees of freedom
## Multiple R-squared:  0.005808,   Adjusted R-squared:  0.0005199 
## F-statistic: 1.098 on 3 and 564 DF,  p-value: 0.3493
\end{verbatim}

\begin{verbatim}
## 
## Call:
## lm(formula = stress ~ hindrance + challenge + resource, data = data22)
## 
## Residuals:
##     Min      1Q  Median      3Q     Max 
## -1.8841 -0.8038 -0.1523  0.7164  2.5693 
## 
## Coefficients:
##              Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  2.383299   0.120392  19.796   <2e-16 ***
## hindrance    0.005571   0.003067   1.816   0.0698 .  
## challenge    0.008445   0.005894   1.433   0.1525    
## resource    -0.004687   0.006068  -0.772   0.4402    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.9678 on 564 degrees of freedom
## Multiple R-squared:  0.01299,    Adjusted R-squared:  0.007741 
## F-statistic: 2.474 on 3 and 564 DF,  p-value: 0.06069
\end{verbatim}

@@

The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout. Additionally, we considered whether resources and challenge demands were perceived as distinct, and finally, whether the patterns were similar across job categories/types of work. The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a). Employers would benefit from understanding that at leas the perception of having ``more'' resources and more challenge demands in a job is highly associated with reported engagement. While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless. The other relationships with outcomes of stress and burnout were not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes. It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
Further, total resources were highly associated challenge demands (supporting H4). We could even argue, given the magnitude of the correlation, that they are capturing the same thing (74\% overlap with a correlation of .86). Need to also talk about our exploratory findings regarding patterns across job type

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?},
  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata Garcia Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{O*Net JDR}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

@@

@@

\abstract{
The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored. 568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources. The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
}

@@

The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes. Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,'' Schaufeli et al., 2002), workplace stress (``an individual state characterized by a combination of high arousal and displeasure,'' p.~15, Pejtersen et al., 2010) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,'' p.~197; Kristensen et al., 2005). Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) would activate a positive state -- that of engagement. In contrast, number of characteristics of one's job appraised as a hindrance demand (i.e., inhibit growth, learning and goal achievement) would activate a negative state -- here, stress.

@@

We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), but from within the unifying framework of O*Net. Here, we focus on the relationship between O*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S. workforce representative sample.

@@

A sample using a Prolific panel resulted in 785 individuals who initially accessed the survey link. Of those,112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021). Additional screening using four embedded attention checks resulted in the retention of respondents. A total of 13.57\% had been in their job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years. Reported ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53). Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%).

@@

Characteristics, Demands, and Resources. Our analyses included items within O*Net's classifications of ``work activity'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'': 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).

Other than minor grammatical editing (for example, changing ``the'' to ``you''), we retained the O*Net wording for our item stems. We used O*Net's response scales, several of which were unique across items, but all shared the same 1 to 5 scale options. Subsequent to providing ratings of whether or not an O*Net characteristic was relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) . . . this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) . . . this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) . . . this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

\begin{quote}
\emph{Stress}. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
\end{quote}

\begin{quote}
\emph{Burnout}. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
\end{quote}

\begin{quote}
\emph{Engagement}. The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α's of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication). For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
\end{quote}

@@

We used R (Version 4.0.3; R Core Team, 2020) and the R-packages careless (Version 1.1.3; Yentes \& Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust \& Barth, 2020), and tinylabels (Barth, 2021) for all analyses. Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands. Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
Correlations, means and standard deviations among all study variables are presented in Table 1. Results reveal a positive association between resources and engagement (\emph{r} = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively). Challenge demands were positively associated with engagement (\emph{r} = .31; H2a), but were unrelated to stress or burnout (H2b and H2c). Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c). To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands. First, regarding engagement (F(3, 564) = 26.41, p \textless{} .001), the total resources (beta = ??) was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table 2). Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, \emph{p} = .060 (see Table 3). Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, \emph{p} = .349. See Table 4.

@@

@@

The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout. The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a). Employers would benefit from understanding that at least the perception of having ``more'' resources and more challenge demands in a job is highly associated with reported engagement. While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless. The other relationships with outcomes of stress and burnout were not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes. It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
